\chapter{Introduction}
This chapter contains general information regarding this document.

\section{Purpose}
%The purpose of this particular STD and its intended readership.
This document contains information regarding the transfer of the \applicationname{} from \projectauthor{} to the client. It describes what is to be transferred, and how these items have been tested before the actual transfer. In chapter \ref{chap:problems}, the state of the transferred items is listed with regards to the user requirements of the URD \cite{urd}.

\section{Scope}
%Scope of the software. Identifies the product by name, explains what the software will do.
The \applicationname{} is an application designed and developed by \projectauthor{} for prof.dr.ir. P.D. Anderson, at the Eindhoven University of Technology. The application serves as an educational tool for anyone who wants to gain a deeper understanding of the process of mixing in general, and in particular for students at the TU/e.

\section{List of definitions}
%The definitions of all used terms, acronyms and abbreviations.
\subsection{Definitions}
\begin{description}
\item[Client:] Prof.dr.ir. P.D. Anderson.
\item[Internet Explorer:] A web browser from Microsoft.
\item[iOS Safari:] A web browser by Apple, designed for mobile iOS devices.
\item[Safari:] A web browser by Apple, designed for Mac devices.
\end{description}

\subsection{Abbreviations}
\begin{tabular}{l|l}
2IP35 & The Software Engineering Project \\
ADD & Architectural Design Document \\
ATP & Acceptance Test Plan \\
DDD & Detailed Design Document \\
ESA & European Space Agency \\
ITP & Integration Test Plan \\
SCMP & Software Configuration Management Plan \\
SPMP & Software Project Management Plan \\
SQAP & Software Quality Assurance Plan \\
SRD & Software Requirements Document \\
STD & Software Transfer Document \\
SUM & Software User Manual \\
SVVP & Software Validation and Verification Plan \\
URD & User Requirements Document \\
UTP & Unit Test Plan \\
TU/e  & Eindhoven University of Technology \\
\end{tabular}

\section{List of references}
\bibliography{../ref}

\section{Overview}
The remainder of this document starts with a description of the build procedures in chapter \ref{chap:build}. The installation procedures for the software built using these build procedures are described in chapter \ref{chap:install}. The list of items transferred to the client is described in chapter \ref{chap:conf}. A summary of the test results obtained by executing the tests in the ATP \cite{atp} is provided in chapter \ref{chap:testreports}. Chapter \ref{chap:problems} lists some problems that were raised during the transfer phase. If any modifications were requested by the customer during the transfer phase, they are listed in chapter \ref{chap:changes}. If these were implemented during the transfer phase, they are documented in chapter \ref{chap:implemented}.
