\chapter{Software Modification Reports}
\label{chap:implemented}
During the transfer phase, the following modifications requests from the customer were implemented

\section*{Storing an empty protocol}
The \emph{Save protocol} button has been disabled when the current protocol is empty.

\section*{Show loading}
The application now shows a small notification when it is loading.

\section*{Stop define protocol inappropriate}
The \emph{Stop define protocol} button has been renamed to \emph{Back}.

\section*{Popups should be centered}
All popups now remain in the centre of the window while resizing.

\section*{Performance graphs should have a logarithmic scale}
The performance graphs now have a logarithmic scale on the y-axis.

\section*{The greyed entries are confused with selected entries}
In the \emph{View multiple performance} option, the greyed entries in the loading menu are now coloured lighter.

\section*{Buttons are sometimes unresponsive}
The buttons have been made slightly bigger and some functionality has been implemented so that buttons respond immediately on the iPad, instead of with a small delay.

\section*{Messages should be out of the way}
Notifications are shown in the upper left corner of the screen now.

\section*{Differently coloured \emph{Back} button}
All \emph{Back} buttons are now coloured differently, namely green, opposed to the blue of the normal buttons.

\section*{Remove the CellBrowser}
The CellBrowser is disabled, the application now loads immediately with the rectangular geometry.

\section*{Initial tutorial distribution}
When the application is started, a `tutorial distribution' is displayed on the canvas, that contains a short description of the functionality of the application.