\chapter{Software Problem Reports}
\label{chap:problems}

The following are all known bugs at the transfer phase.

\section{Popups}

\subsection*{Issue}
When a popup pops up, other buttons still appear clickable while they are not.

\subsection*{Solution}
When the popup pops up, there should be a darker overlay under the popup that covers the screen.

\section{Compare performance}

\subsection*{Issue}
When the local storage is full, the graph for comparing performance of multiple mixing runs fails to load.

\subsection*{Solution}
When the local storage is full, the graph should load normally.

\section{Delete confirmation}

\subsection*{Issue}
When deleting files, no confirmation popup shows up before deleting. This is to prevent users from accidentally deleting files.

\subsection*{Solution}
When a file is to be deleted, a popup should show up to confirm the removal.

\section{Full local storage}

\subsection*{Issue}
When saving something, no warning is given when the local storage is full.

\subsection*{Solution}
If the local storage is full when saving, a warning should be given that the local storage is full.

\section{Internet Explorer}

\subsection*{Issue}
In Internet Explorer, performance graphs fail to be drawn.

\subsection*{Solution}
Get the gwt-visualization.jar library to work for Internet Explorer.

\section{Resizing}

\subsection*{Issue}
If the application is resized to a size smaller than the canvas, the browser chrashes.

\subsection*{Solution}
The application should resize properly.

\section{Safari exporting}

\subsection*{Issue}
In Safari, images cannot be exported properly.

\subsection*{Solution}
Exporting in Safari can be enabled by sending the to be downloaded file to the server, and downloading it from there.

\section{Memory leak}

\subsection*{Issue}
The Fortran module allocates memory it doesn't de-allocate later. This causes the application to run out of memory after some uptime.

\subsection*{Solution}
The Fortran module should de-allocate all its used memory.
