\chapter{Software Change Requests}
\label{chap:changes}

In this chapter, requests that emerged during the transfer phase are listed.

\section*{Storing an empty protocol}
Storing an empty protocol is currently possible. The \emph{Save} button that saves a protocol should be disabled when the protocol is empty.

\section*{Show loading}
When the application is loading a concentration distribution, the program should display that it is busy loading.

\section*{Stop define protocol inappropriate}
The \emph{Stop define protocol} button in the protocol menu should be called \emph{Back}, to be consistent with the other \emph{Back} buttons.

\section*{Popups should be centered}
Popups should be centered, even when the window is resized.

\section*{Performance graphs should have a logarithmic scale}
The performance graphs should have a logarithmic scale on the \emph{y-axis}.

\section*{The greyed entries are confused with selected entries}
In the \emph{View multiple performance} option, the greyed entries in the loading menu are confused with selected entries. The selected entries should be more distinguishable from the grey entries.

\section*{Buttons are sometimes unresponsive}
Sometimes button presses are not registered, this could be alleviated by making the buttons bigger.

\section*{Responsive CellLists}
While the buttons are now fast, the CellLists used for loading are still slow. They should be sped up.

\section*{Messages should be out of the way}
Messages for \emph{Save/Delete successful} should be in the corner of the screen, where they do not block buttons.

\section*{Differently coloured \emph{Back} button}
The \emph{Back} buttons should be coloured differently, to make them stand out.

\section*{Remove the CellBrowser}
With only a single geometry, the CellBrowser is rather useless, therefore it should be removed.

\section*{Initial tutorial distribution}
When the application is started, it is unclear how the walls function. For this purpose, a `tutorial distribution' should be made. This tutorial distribution should explain how the walls can be used for mixing.